---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ``` {mapcdatakeys} ```

<!-- badges: start -->
<!-- badges: end -->

This package contains two kinds of components:

### Data Keys

These data keys are created at the municipal, census block, block group and tract level. As Census geographies can change between two decadal counts, they have two kinds of crosswalks - geographical, and weighted. For these, we provide two functions described below.

*Please raise an issue if you would like any additions, or alterations to this package which we can incorporate.*

Detailed descriptions of each geographic level of data keys can be found on their individual pages below:

* [Municipal Level Keys](municipal_level_keys.md)

* [Keys for Census Geographies](census_geog_keys.md)

### Functions to call crosswalks

These two functions are used to call specific crosswalks based on either their vintage, and/or the relevant geographic unit.

* [Crosswalk Functions](crosswalk_functions.md)


This package obtains standardized data keys for four different geographic levels in Massachusetts.


## Installation

You can install the released version of ```mapcdatakeys``` with:

``` r
# install.packages("devtools")
devtools::install_github("MAPC/mapcdatakeys")
```
## Examples for 

Load the package with this line:

```{r example}
library(mapcdatakeys)

head(mapcdatakeys::mbta_data_keys)

```

Incredible help from Desiree De Leon and Alison Hill from their [rstudio4edu handbook, chapter 12](https://rstudio4edu.github.io/rstudio4edu-book/data-pkg.html)